---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(broom)
library(shiny)
library(lubridate)
library(sugrrants)
library(leaflet)
library(ggmap)
library(here)
library(mapview)
library(broom)
library(stringr)
library(kableExtra)
```

```{r loading-data}
parking2019_tidy <- read.csv(here::here("parking2019_tidy.csv")) %>% mutate(sign_rule = strtrim(Sign, 6), arr_date = date(arr_date))

top10_table <- read_csv("Top10_Melb_Count.csv")

hols_2019 <- tsibble::holiday_aus(year = 2019, state = "VIC")

#create dataset for holidays related to arr_date
park_2019_hols <- parking2019_tidy %>% 
  mutate(weekday = wday(arr_date, label = TRUE, week_start = 1),
         workday = if_else(
           condition = arr_date %in% hols_2019$date | weekday %in% c("Sat", "Sun"),
           true = "holidays",
           false = "workday"))
```


Overview
===========================
Column {data-width=400}
-----------------------------------------------------------------------
### Top 10 Busiest Parking Street in Melbourne
```{r top-10}
top10_table <- read_csv("Top10_Melb_Count.csv")
knitr::kable(top10_table, caption = "Top 10 busiest parking street in Melbourne") %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```


Column {data-width=400}
-----------------------------------------------------------------------

### Map of 10 Busiest Parking Street in Melbourne

```{r bincol-cor-info}
coord <- data_frame("lat" = c(-37.8147255,
                              -37.8192437,
                              -37.8101661,
                              -37.8183015,
                              -37.8156404,
                              -37.809040,
                              -37.8140175,
                              -37.8153781,
                              -37.8075632,
                              -37.816335),
                    "lon"=c(144.952553,
                            144.9553465,
                            144.9687394,
                            144.9811929,
                            144.976875,
                            144.969121,
                            144.9692056,
                            144.9531639,
                            144.9532773,
                            144.978169))

info <- data_frame("info" = c("Lonsdale Street is one of the main streets in Melbourne's CBD. It offers high rise apartment style living, in amongst the areas businesses, shopping centres and hotels. China Town extends through a number of smaller alleys between Lonsdale and Bourke.",
"King Street is a key hub of Melbourne's nightlife and is home to many pubs, nightclubs, restaurants, and adult entertainment venues",
"Lonsdale Street is one of the main streets in Melbourne's CBD. It offers high rise apartment style living, in amongst the areas businesses, shopping centres and hotels. China Town extends through a number of smaller alleys between Lonsdale and Bourke.",
"Jolimont Street features parks, business precincts and a limited amount of residential accommodation. It's close to Fitzroy Garden and Melbourne Cricket Ground",
"Jolimont Street features parks, business precincts and a limited amount of residential accommodation. It's close to Fitzroy Garden and Melbourne Cricket Ground",
"In Exhibition Street there a lot of luxurious hotels eg Marriott Hotel & Rydges Hotel. It also the heart of working district",
"In Exhibition Street there a lot of luxurious hotels eg Marriott Hotel & Rydges Hotel. It also the heart of working district",
"King Street is a key hub of Melbourne's nightlife and is home to many pubs, nightclubs, restaurants, and adult entertainment venues",
"William Street is a major street in the city, there are notable landmarks on William Street include the Queen Victoria Market, the Flagstaff Gardens, Immigration Museum, Supreme Court of Victoria, AMP Square",
"Wellington Parade South, it's located between parks and residential building"))

top10_cor_info <- bind_cols(top10_table, coord, info)
write_csv(top10_cor_info, "Top10_Melb_Cor_Info.csv")
```

```{r leaflet_markers}
top10_leaflet <- read_csv("Top10_Melb_Cor_Info.csv")

getColor <- function(table) {
  sapply(table$CountperDay, function(CountperDay) {
  if(CountperDay <= 350) {
    "green"
  } else if(CountperDay <= 450) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(top10_leaflet)
) 

l <- leaflet(data = top10_leaflet[1:10,])

l %>%
addTiles() %>%
addAwesomeMarkers(~lon, ~lat, icon=icons, popup = ~as.character(info), label=~as.character(StreetName))
```

Calendar plot
===========================
Column {data-width=200}
-----------------------------------------------------------------------

### User interactions

```{r calendar-controls, echo = FALSE}
# date range inputs
start_date <- ymd("2019-01-01")
end_date <- ymd("2019-12-31")

daterange_ui <- dateRangeInput(
  "selected_dates", 
  "Select Dates for Calendar Display", 
  start = start_date, 
  end = end_date, 
  min = min(park_2019_hols$arr_date), 
  max = max(park_2019_hols$arr_date)
)

daterange_ui

violation_ui <- selectInput(inputId = "colour_lines",
                       label = "Colour lines",
                       selected = "workday",
                       choices = c("workday", "InViolation"))

violation_ui
```



Column {data-width=600}
-----------------------------------------------------------------------
### Calendar plot
```{r calendarise, echo=FALSE}
park_date <- reactive({
  start_date <- input$selected_dates[1]
  end_date <- input$selected_dates[2]
  park_2019_hols %>% 
    filter(between(arr_date, start_date, end_date))
})

selected_colour <- reactive({
  sym(input$colour_lines)
})


calenderise <- reactive({
  
  park_date <- park_date()
  
    frame_calendar(park_date,
                   x = arr_hour,
                 y = DurationMinutes,
                 date = arr_date)
})


```

```{r draw-calendar, out.width="100%"}
renderPlot({
  calendar <- calenderise()
  
  colour <- selected_colour()
  
    gg_cal <- ggplot(calendar, 
                     aes(x = .arr_hour,
                         y = .DurationMinutes,
             group = arr_date)) +
  geom_line(aes(colour = !!colour)) +
  theme(legend.position = "bottom")
    
prettify(gg_cal)
})
```

### Workdays vs Non-workdays
```{r workdays-vs-non-work}
renderPlot({
 ggplot(park_2019_hols,
       aes(x = as.factor(arr_hour),
           y = DurationMinutes,
             # Because there are duplicate date in different months, so we use this
           colour = sign_rule) 
       )+
  geom_boxplot(size = 0.3,
            alpha = 0.8) +
  facet_grid(sign_rule~workday,
             labeller = labeller(StreetName = label_wrap_gen(20))) +
  scale_colour_brewer(palette = "Set2", name = "sign_rule") +
  scale_y_continuous(breaks = c(seq(from = 0, to = 200, by = 20)),
                     limits = c(0, 200)) +
  theme(legend.position = "none")+
  labs(x = "Time Hour")
})
```



Trend in Lonsdale Street
===========================
Column {data-width=200}
-----------------------------------------------------------------------
### User interactions {data-height=300}

```{r user-controls, echo = FALSE}
street_ui <- selectInput(inputId = "street_id",
                       label = "Choose BetweenStreet1",
                       selected = "all",
                       choices = c("all", "EXHIBITION STREET", "KING STREET", "QUEEN STREET", "RUSSELL STREET", "WILLIAM STREET"))

street_ui
```

### Summary of parking duration {data-heigh=500}

```{r avgduration_sign}
parking2019_tidy %>% 
  group_by(sign_rule) %>%
  summarise(avg_duration = mean(DurationMinutes)) %>%
  kable() %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```

```{r avgduration_betweenstreet}
parking2019_tidy %>% 
  group_by(BetweenStreet1) %>%
  summarise(avg_duration = mean(DurationMinutes)) %>%
  kable() %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```

Column {data-width=600}
-----------------------------------------------------------------------
### Temporal Patterns
```{r plot-temporal-patterns}
park_2019_hols2 <- park_2019_hols %>%
  group_by(arr_date, sign_rule, BetweenStreet1) %>%
  summarise(mean_duration = mean(DurationMinutes))

street <- reactive({
  street_filtered <- park_2019_hols2
  
  if(input$street_id != 'all')
  street_filtered <- park_2019_hols2 %>%
    filter(BetweenStreet1 == input$street_id)
  
  street_filtered
})
  
 
renderPlot({
  ggplot(street(),
    aes(x = arr_date,
             y = mean_duration,
             colour = sign_rule)) +
  geom_line(size = 0.3) +
  facet_grid(sign_rule ~ BetweenStreet1,
             # this code presents the facets in a nice way
             labeller = labeller(SignPlateID = label_wrap_gen(20))) +
  # this code mades the x axis a bit nicer to read
  scale_x_date(date_labels = "%d %b %Y",
               date_minor_breaks = "1 month") +
  scale_colour_brewer(palette = "Set2") +
  labs(x = "Date Time") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none")
})
```

Parking Signs Violations
===========================
### Proportion of vehicles in violation of parking restriction
```{r summary-violations}
summ_parking2019_vio <- parking2019_tidy %>%
  group_by(InViolation) %>%
  summarise(total = sum(n())) 
  
kable(summ_parking2019_vio) %>%
  kable_styling(bootstrap_options = "bordered")
```

### Adjacent streets with the most restriction violations
```{r parking-violation}
parking2019_vio <- parking2019_tidy %>%
  filter(InViolation == "true")
```

```{r}
parking2019_vio %>%
  group_by(BetweenStreet1) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```

### Top 10 most common parking signs which are violated
```{r}
parking2019_vio %>%
  group_by(BetweenStreet1, Sign) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```


Trends for Overstayed Vehicles
===========================
### Overstayed Vehicles

```{r}
parking2019_vio <- parking2019_vio %>%
  # Extract specfic signs, assign them according to minutes
  mutate(restrict_mins = case_when(
    str_starts(Sign, "1/2 P") ~ 30, 
    str_starts(Sign, "1P") ~ 60,
    str_starts(Sign, "2P") ~ 120),
  # Extract parking signs, assign them into respective factors 
    restriction = case_when(
    str_starts(Sign, "1/2 P") ~ "1/2P", 
    str_starts(Sign, "1P") ~ "1P",
    str_starts(Sign, "2P") ~ "2P"
    ),
    # Compute amount of mins overstayed
    overstay_mins = DurationMinutes - restrict_mins)
```

```{r}
require(ggridges)
renderPlot({
ggplot(parking2019_vio) +
  geom_density_ridges(
    aes(
      x = overstay_mins,
      y = factor(restriction),
      fill = factor(restriction)
    ),
    alpha = 0.6,
    stat = "binline",
    bins = 45
  ) +
  scale_x_continuous(breaks = c(seq(from = 0, to = 300, by = 10)),
                     limits = c(0, 300)) +
  facet_wrap( ~ BetweenStreet1, nrow = 3) +
  scale_fill_manual(values = c("#663300", "#006633", "#330066")) +
  labs(x = "Minutes overstayed", y = "") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 12, 
                                    face = "bold", 
                                    margin = unit(c(1.5, 0, 0, 0), "lines"))) +
  ggtitle("Density estimate of vehicles who overstayed restrictions")
})
```

### Trend of Overstayed Vehicles

```{r}
parking2019_vio <- parking2019_vio %>%
  # Retrieve day of the week 
  mutate(arr_day = wday(arr_date, label = TRUE, week_start = 1),
         dep_day = wday(dep_date, label = TRUE, week_start = 1))
```

```{r}
parking2019_plot2 <- parking2019_vio 
# Format CHAR to TIME variable  
parking2019_plot2$arr_time <- 
  as.POSIXct(parking2019_plot2$arr_time, format="%H:%M")
parking2019_plot2$dep_time <-
  as.POSIXct(parking2019_plot2$dep_time, format="%H:%M")
parking2019_plot2 <- parking2019_plot2 %>%
  # Group arrival and departure times as arr_dep variable
    pivot_longer(c(arr_time, dep_time), 
               names_to = "arr_dep",
               values_to = "arr_dep_time")
```

```{r analysis2}
renderPlot({
parking2019_plot2 %>% ggplot() +
  geom_violin(
    aes(x = arr_day, y = arr_dep_time, colour = arr_dep),
    scale = "count",
    alpha = 0.6,
    draw_quantiles = 0.5
  ) +
  facet_wrap(~ BetweenStreet1, nrow = 3) +
  scale_colour_manual(values = c("#00468b", "#009700")) +
  labs(x = "Arrival/Departure Time", y = "") +
  theme(legend.position = "bottom")
})
```


Predict
===========================
Column {data-width=400}
------------------------------------

### Model building
We _fit_ a _linear model_ on log-transformed duration for 2019, using a four-way interaction: arrival hour, work day or non-work day, signPlateID, and sign rule.

$log(DurationMinutes + 1) =  arr hour_i \times weekday_i \ SignPlateID_i \times signrule_i$

where arr_hour is a continuous variable, and the other three are categorical variables. 

This model explains 11.17% of the variation in the data.

### Residual
```{r res-fitted}
# Residual vs plot

renderPlot({
park_aug_lm %>% 
  ggplot(aes(x = .fitted,
             y = .resid)) +
  geom_point() +
  facet_wrap(~StreetName)+
  geom_abline(size = 2, color = "darkred")
})
```


Column {data-width=400}
------------------------------------

### Predicted versus observed usage {data-height=400}
```{r process-walking-data}
park19_lm <- park_2019_hols %>% 
  mutate_at(.vars = vars(StreetName,
                         SignPlateID,
                         sign_rule,
                         arr_hour,
                         workday
                          ),
            as_factor) %>% 
  mutate(log_duration = log1p(DurationMinutes))
```

```{r fit-lm}
  park_fit_lm <- lm (
    formula = log_duration ~ arr_hour + weekday + SignPlateID + sign_rule,
    data = park19_lm
  )
```

```{r glance-fit-lm}
# Extract model fit summary
glance(park_fit_lm)

#model-augment
park_aug_lm <- augment(park_fit_lm, data = park19_lm)

renderPlot({
ggplot(park_aug_lm,
       aes(x = .fitted,
       y = log_duration,
       color = sign_rule)) +
  geom_point(alpha = 0.4)+
  geom_smooth(method= "lm", size = 2, color = "yellow", se= FALSE)+
  labs(color = "Sign Rule")
})
```

Explain
===========================
Column {data-width=400}
-----------------------------------------------------------------------
### Data
Our dataset shows the records of cars parking in the streets of Melbourne CBD in 2019. For each parking lots, there will be sensors in it to track when a vehicle arrives and departs.

Each record includes the restriction of the bay and whether the vehicle overstayed that restriction. An event will also state the time that the parking lot is empty or vacant. 

```{r}
parking2019_tidy <- read.csv("parking2019_tidy.csv")
parking2019_tidy
#should we put in the original dataset instead?
```

Column {data-width=400}
-----------------------------------------------------------------------
### Making a model and predictions
We also fitted a linear model to the data.


Data cleaning
===========================
Here are the code that we used for cleaning and wrangling the data. 

     #Retrieve Lonsdale street and its between streets_
      parking2019_tidy <- parking2019 %>%  
      
    #Retrieve Lonsdale Street data  
    #Remove parking lots without parking signs  
      filter(StreetName == "LONSDALE STREET",
         !(is.na(Sign))) %>%   
    
    #Separate date and time variables  
    separate(ArrivalTime, into = c("arr_date", "arr_time"), sep =" ") %>%
    separate(DepartureTime, into = c("dep_date", "dep_time"), sep = " ")  
      
    #Format date variables from CHAR to DATE  
    parking2019_tidy$arr_date <- mdy(parking2019_tidy$arr_date)  
    parking2019_tidy$dep_date <- mdy(parking2019_tidy$dep_date)  
      
    #Extract hour& minutes  
    parking2019_tidy$arr_hour <-    format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%H")  
    parking2019_tidy$arr_min <- 
    format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%M")  
    parking2019_tidy$dep_hour <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M:%S"),"%H")  
    parking2019_tidy$dep_min <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%M")  
    parking2019_tidy$arr_time <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%H: %M")  
    parking2019_tidy$dep_time <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M:%S"),"%H: %M")  

    #remove unrelated variables_  
    parking2019_tidy <- parking2019_tidy %>%
    select(-DeviceId,
         -StreetMarker,
         -StreetId,
         -BetweenStreet2,
         -BetweenStreet2ID,
         -AreaName)


References
===========================
Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of
  Data Manipulation. R package version 0.8.5. https://CRAN.R-project.org/package=dplyr

  Hadley Wickham, Jim Hester and Romain Francois (2018). readr: Read Rectangular Text Data. R
  package version 1.3.1. https://CRAN.R-project.org/package=readr
  
  Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
  https://doi.org/10.21105/joss.01686
  
   Garrett Grolemund, Hadley Wickham (2011). Dates and Times Made Easy with lubridate. Journal of
  Statistical Software, 40(3), 1-25. URL http://www.jstatsoft.org/v40/i03/.
  
   Wang, E, D Cook, and RJ Hyndman (2020). A new tidy data structure to support exploration and
  modeling of temporal data. Journal of Computational and Graphical Statistics.
  doi:10.1080/10618600.2019.1695624.
  
    Joe Cheng, Bhaskar Karambelkar and Yihui Xie (2019). leaflet: Create Interactive Web Maps with
  the JavaScript 'Leaflet' Library. R package version 2.0.3.
  https://CRAN.R-project.org/package=leaflet
  
   D. Kahle and H. Wickham. ggmap: Spatial Visualization with ggplot2. The R Journal, 5(1),
  144-161. URL http://journal.r-project.org/archive/2013-1/kahle-wickham.pdf
  
   Kirill Müller (2017). here: A Simpler Way to Find Your Files. R package version 0.1.
  https://CRAN.R-project.org/package=here
  
  David Robinson and Alex Hayes (2020). broom: Convert Statistical Analysis Objects into Tidy
  Tibbles. R package version 0.5.6. https://CRAN.R-project.org/package=broom
  
  Hadley Wickham (2019). stringr: Simple, Consistent Wrappers for Common String Operations. R
  package version 1.4.0. https://CRAN.R-project.org/package=stringr
  
  Hao Zhu (2019). kableExtra: Construct Complex Table with 'kable' and
  Pipe Syntax. R package version 1.1.0.
  https://CRAN.R-project.org/package=kableExtra
  
  Claus O. Wilke (2020). ggridges: Ridgeline Plots in 'ggplot2'. R
  package version 0.5.2. https://CRAN.R-project.org/package=ggridges
  
  City of Melbourne Open Data Team. (n.d.). On-street Car Parking Sensor Data - 2019 | Open Data | Socrata. Retrieved June 4, 2020, from https://data.melbourne.vic.gov.au/widgets/7pgd-bdf2