---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(broom)
library(shiny)
library(lubridate)
library(sugrrants)
library(leaflet)
library(ggmap)
library(here)
library(mapview)
library(broom)
library(stringr)
```

```{r loading-data}
parking2019_tidy <- read.csv(here::here("parking2019_tidy.csv")) %>% 
  mutate(sign_rule = strtrim(Sign, 3), arr_date = date(arr_date))

top10_table <- read_csv("Top10_Melb_Count.csv")

hols_2019 <- tsibble::holiday_aus(year = 2019, state = "VIC")

#create dataset for holidays related to arr_date
park_2019_hols <- parking2019_tidy %>% 
  mutate(weekday = wday(arr_date, label = TRUE, week_start = 1),
         workday = if_else(
           condition = arr_date %in% hols_2019$date | weekday %in% c("Sat", "Sun"),
           true = "holidays",
           false = "workday"))
```


Overview
===========================

Column {data-width=300}
-----------------------------------------------------------------------

### User interactions?

```{r calendar-controls, echo = FALSE}
# date range inputs
start_date <- ymd("2019-01-01")
end_date <- ymd("2019-12-31")

daterange_ui <- dateRangeInput(
  "selected_dates", 
  "Select Dates for Calendar Display", 
  start = start_date, 
  end = end_date, 
  min = min(park_2019_hols$arr_date), 
  max = max(park_2019_hols$arr_date)
)

daterange_ui

violation_ui <- selectInput(inputId = "colour_lines",
                       label = "Colour lines",
                       selected = "workday",
                       choices = c("workday", "InViolation"))

violation_ui


sign_ui <- selectInput(inputId = "sign_id",
                       label = "Choose sign",
                       selected = "all",
                       choices = c("1/2", "1P", "2P", "P D"))

sign_ui
```

Column {data-width=400}
-----------------------------------------------------------------------
### Calendar plot
```{r calendarise, echo=FALSE}
park_date <- reactive({
  start_date <- input$selected_dates[1]
  end_date <- input$selected_dates[2]
  park_2019_hols %>% 
    filter(between(arr_date, start_date, end_date))
})

selected_colour <- reactive({
  sym(input$colour_lines)
})


calenderise <- reactive({
  
  park_date <- park_date()
  
    frame_calendar(park_date,
                   x = arr_hour,
                 y = DurationMinutes,
                 date = arr_date)
})


```

```{r draw-calendar, out.width="100%"}
renderPlot({
  calendar <- calenderise()
  
  colour <- selected_colour()
  
    gg_cal <- ggplot(calendar, 
                     aes(x = .arr_hour,
                         y = .DurationMinutes,
             colour = workday,
             group = arr_date)) +
  geom_line(aes(colour = !!colour)) +
  theme(legend.position = "bottom")
    
prettify(gg_cal)
})
```

### Temporal Patterns
```{r plot-temporal-patterns}
park_date <- reactive({
  start_date <- input$selected_dates[1]
  end_date <- input$selected_dates[2]
  park_2019_hols %>% 
    filter(between(arr_date, start_date, end_date))
})

sign <- reactive({
  
    if(input$sign_id != 'both')
    {parking2019_tidy}
    
    else{
      parking2019_tidy %>%
        filter(sign_rule == input$sign_id)}
})
```

```{r plot, out.width="100%"}
renderPlot({
  park_date <- park_date()
  
  sign <- sign()
  
   ggplot(sign, aes(x = as.Date(arr_date),
                       y = DurationMinutes,
                       color = sign_rule)) +
        geom_line(size=0.3) +
        facet_grid(sign_rule ~ StreetName,
                   labeller = labeller(signPlateID = label_wrap_gen(20))) +
            scale_x_date(date_labels = "%d %b %Y", 
                   date_minor_breaks = "1 month")+
    scale_colour_brewer(palette = "Set2", name = "sign_rule")+
    labs(x = "Date Time")
 
})
```

Column {data-width=200}
-----------------------------------------------------------------------

### Top 10 Busiest Parking Street in Melbourne

```{r}
knitr::kable(top10_table) %>%
kableExtra::kable_styling(bootstrap_options = "basic")
```

### Map of 10 Busiest Parking Street in Melbourne

```{r}
coord <- data_frame("lat" = c(-37.8147255,
                              -37.8192437,
                              -37.8101661,
                              -37.8183015,
                              -37.8156404,
                              -37.809040,
                              -37.8140175,
                              -37.8153781,
                              -37.8075632,
                              -37.816335),
                    "lon"=c(144.952553,
                            144.9553465,
                            144.9687394,
                            144.9811929,
                            144.976875,
                            144.969121,
                            144.9692056,
                            144.9531639,
                            144.9532773,
                            144.978169))


top10cor <- bind_cols(top10_table,coord)

# Map for locations
cb_bbox <- make_bbox(lon = top10cor$lon,
                     lat = top10cor$lat,
                     f = 0.9)  

best_locations = leaflet() %>%
  # Base group
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%
  # Add reciever location data
  addCircles(
    lng = top10cor$lon,
    lat = top10cor$lat, 
    fill=TRUE, color="red",
    weight= 5,
    radius = 2,
    stroke = FALSE, fillOpacity = 1)

getColor <- function(table) {
  sapply(table$CountperDay, function(CountperDay) {
  if(CountperDay <= 350) {
    "green"
  } else if(CountperDay <= 450) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(top10cor)
) 

leaflet(data = top10cor[1:10,]) %>%
  addTiles() %>%
addAwesomeMarkers(~lon, ~lat, icon=icons, popup = ~as.character(StreetName), label=~as.character(StreetName))
```



Predict
===========================

Column {data-width=400}
------------------------------------

### Model building
We _fit_ a _linear model_ on log-transformed duration for 2019, using a four-way interaction: arrival hour, work day or non-work day, signPlateID, and sign rule.

$log(DurationMinutes + 1) =  arr hour_i \times weekday_i \ SignPlateID_i \times signrule_i$

where arr_hour is a continuous variable, and the other three are categorical variables. 

This model explains 43% of the variation in the data.

Column {data-width=400}
------------------------------------

### Predicted versus observed usage {data-height=400}
```{r process-walking-data}
park19_lm <- park_2019_hols %>% 
  mutate_at(.vars = vars(StreetName,
                         SignPlateID,
                         sign_rule,
                         arr_hour,
                         workday
                          ),
            as_factor) %>% 
  mutate(log_duration = log1p(DurationMinutes))
```

```{r fit-lm}
  park_fit_lm <- lm (
    formula = log_duration ~ arr_hour + weekday + SignPlateID + sign_rule,
    data = park19_lm
  )
  # statistic variables
  park_fit_lm
```

```{r glance-fit-lm}
# Extract model fit summary
glance(park_fit_lm)
```

```{r aug-broom-plot}
park_aug_lm <- augment(park_fit_lm, data = park19_lm)
ggplot(park_aug_lm,
       aes(x = .fitted,
       y = log_duration,
       color = sign_rule)) +
  geom_point(alpha = 0.4)+
  geom_smooth(method= "lm", size = 2, color = "yellow", se= FALSE)+
  labs(color = "Sign Rule")
```


Explain
===========================
Column {data-width=400}
-----------------------------------------------------------------------
### Data
Our dataset shows the records of cars parking in the streets of Melbourne CBD in 2019. For each parking lots, there will be sensors in it to track when a vehicle arrives and departs.

Each record includes the restriction of the bay and whether the vehicle overstayed that restriction. An event will also state the time that the parking lot is empty or vacant. 

```{r}
parking2019_tidy <- read.csv("parking2019_tidy.csv")
parking2019_tidy
#should we put in the original dataset instead?
```

Column {data-width=400}
-----------------------------------------------------------------------
### Making a model and predictions
We also fitted a linear model to the data.


Data cleaning
===========================
Here are the code that we used for cleaning and wrangling the data. 

     #Retrieve Lonsdale street and its between streets_
      parking2019_tidy <- parking2019 %>%  
      
    #Retrieve Lonsdale Street data  
    #Remove parking lots without parking signs  
      filter(StreetName == "LONSDALE STREET",
         !(is.na(Sign))) %>%   
    
    #Separate date and time variables  
    separate(ArrivalTime, into = c("arr_date", "arr_time"), sep =" ") %>%
    separate(DepartureTime, into = c("dep_date", "dep_time"), sep = " ")  
      
    #Format date variables from CHAR to DATE  
    parking2019_tidy$arr_date <- mdy(parking2019_tidy$arr_date)  
    parking2019_tidy$dep_date <- mdy(parking2019_tidy$dep_date)  
      
    #Extract hour& minutes  
    parking2019_tidy$arr_hour <-    format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%H")  
    parking2019_tidy$arr_min <- 
    format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%M")  
    parking2019_tidy$dep_hour <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M:%S"),"%H")  
    parking2019_tidy$dep_min <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%M")  
    parking2019_tidy$arr_time <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M:%S"),"%H: %M")  
    parking2019_tidy$dep_time <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M:%S"),"%H: %M")  

    #remove unrelated variables_  
    parking2019_tidy <- parking2019_tidy %>%
    select(-DeviceId,
         -StreetMarker,
         -StreetId,
         -BetweenStreet2,
         -BetweenStreet2ID,
         -AreaName)


References
===========================