---
title: "Untitled"
author: "Putu Wahyu Saputra"
date: "6/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE, cache=TRUE)
```

```{r libraries}
library(dplyr)
library(readr)
library(tidyverse)
library(lubridate)
library(tsibble)
library(sugrrants)



```

```{r read}
park19 <- read_csv("park19_tidy.csv")

park19
```

# Section 1 : What is the proportion of vehicles that overstayed for a given restriction? 1/2p,1p,2p,3p,4p

# Section 2 : What are the time frames where parking lots are the most vacant/occupied?

# Section 3 : Parking availability: On a workday/non-workday, what are the time frames where parking lots are the most vacant/occupied? 

```{r} 

hols_2019 <- tsibble::holiday_aus(year = 2019, state = "VIC")

#create dataset for holidays related to arr_date
park_2019_hols <- park19 %>% 
  mutate(weekday = wday(arr_date, label = TRUE, week_start = 1),
         workday = if_else(
           condition = arr_date %in% hols_2019$date | weekday %in% c("Sat", "Sun"),
           true = "holidays",
           false = "workday"))

```

```{r workdays-vs-non-work}
ggplot(park_2019_hols,
       aes(x = as.factor(arr_hour),
           y = DurationMinutes,
            group = arr_date, # Because there are duplicate date in different months, so we use this
           # colour = SignPlateID) 
       ))+
  geom_line(size = 0.3,
            alpha = 0.3) +
  facet_grid(SignPlateID~workday,
             labeller = labeller(StreetName = label_wrap_gen(20))) +
  scale_colour_brewer(palette = "Set2", name = "SignPlateID") +
  theme(legend.position = "none")
```

SignPlateID 3 only Sunday
SignPlateID 583 is for disability (never occupied)
SignPlateID 508 is Mon-Sat 6.30 to 20.30 (small window)

```{r}
plat_508 <- park_2019_hols %>%
  select(arr_date, arr_hour, workday, SignPlateID, Sign, DurationMinutes) %>% 
  filter(SignPlateID == 508) %>%
  group_by(arr_date, workday, arr_hour)

plat_508
ggplot(plat_508,
       aes(x = as.factor(arr_hour),
           y = DurationMinutes,
            group = arr_date, # Because there are duplicate date in different months, so we use this
                  ))+
  geom_line(size = 0.3,
            alpha = 0.3) +
  facet_grid(~workday,
             labeller = labeller(StreetName = label_wrap_gen(20))) +
  scale_colour_brewer(palette = "Set2", name = "StreetName") +
  theme(legend.position = "none")
```


```{r calendar-plot}

russel_cal <- park_2019_hols %>% 
  frame_calendar(x = arr_hour,
                 y = DurationMinutes,
                 date = arr_date)

gg_cal <- russel_cal %>% 
  ggplot(aes(x = .arr_hour,
             y = .DurationMinutes,
             colour = workday,
             group = arr_date)) +
  geom_line()

prettify(gg_cal) +
  theme(legend.position = "bottom")
```

# Section 4 : There any prominent characteristics for the top 10 hardest parking street to get in Melbourne CBD?  **we need a new dataset here**


# DEADLINE : TOMORROW