---
title: "Parking in Melbourne"
author: "Brendi Ang, Dea Vega Editya, Helen Evangelina, Putu Wahyu Saputra"
date: "6/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, cache=TRUE)
```

```{r libraries}
library(dplyr)
library(kableExtra)
library(readr)
library(tidyverse)
library(lubridate)
library(tsibble)
library(sugrrants)
library(leaflet)
library(ggmap)
library(ggridges)
library(here)
library(mapview)
library(broom)
library(stringr)
library(kableExtra)
library(ggpubr)
```

# Data wrangling

```{r read-in, cache = TRUE}
parking2019 <- read.csv(here::here("On-street_Car_Parking_Sensor_Data_-_2019.csv"))
```

```{r}
parking2019_tidy <- parking2019 %>%
  filter(StreetName == "LONSDALE STREET",
         !(is.na(SignPlateID))) %>%  
  select(-DeviceId,
         -StreetMarker,
         -StreetId,
         -BetweenStreet2,
         -BetweenStreet2ID,
         -AreaName) %>%
  separate(ArrivalTime, into = c("arr_date", "arr_time"), sep =" ", extra = "merge") %>% 
  separate(DepartureTime, into = c("dep_date", "dep_time"), sep =" ", extra = "merge")

# Format time into 24-hour format
parking2019_tidy$arr_time <- format(strptime(parking2019_tidy$arr_time, "%I:%M:%S %p"), "%H:%M")
parking2019_tidy$dep_time <- format(strptime(parking2019_tidy$dep_time, "%I:%M:%S %p"), "%H:%M")

# Format date variables from CHAR to DATE 
parking2019_tidy$arr_date <- mdy(parking2019_tidy$arr_date)
parking2019_tidy$dep_date <- mdy(parking2019_tidy$dep_date)

# Extract hour& minutes 
parking2019_tidy$arr_hour <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M"),"%H")
parking2019_tidy$arr_min <- 
format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M"),"%M")
parking2019_tidy$dep_hour <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M"),"%H")
parking2019_tidy$dep_min <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M"),"%M")
parking2019_tidy$arr_time <- format(as.POSIXct(parking2019_tidy$arr_time,format="%H:%M"),"%H: %M")
parking2019_tidy$dep_time <- format(as.POSIXct(parking2019_tidy$dep_time,format="%H:%M"),"%H: %M")
```

```{r read-in-tidy-data, cache = TRUE}
parking2019_tidy <- write_csv(parking2019_tidy, "parking2019_tidy.csv")
```


# Section 1 : What is the proportion of vehicles that overstayed for a given restriction? 1/2p,1p,2p,3p,4p
```{r summary-violations}
summ_parking2019_vio <- parking2019_tidy %>%
  group_by(InViolation) %>%
  summarise(total = sum(n())) 
  
kable(summ_parking2019_vio,
      caption = "Proportion of vehicles in violation of parking restriction") %>%
  kable_styling(bootstrap_options = "bordered")
```

> Parking Services Officers may mark the tire of a vehicle parked in a time-restricted area& come back as soon as you overstay the time restriction.
> Inside Melbourne CBD, the parking fees for on street-parking is [$7/hr](https://www.melbourne.vic.gov.au/parking-and-transport/parking/parking-locations-fees/Pages/parking-locations-and-fees.aspx).
Data:
> In 2019, a total of 249,216 instances where a car parked& departed.
> Of this, 10,191 (2.918%) violated the restriction.
> This proportion may seem little, but parking fines are on average, [$124](https://www.melbourne.vic.gov.au/parking-and-transport/parking/parking-fines/Pages/default.aspx#:~:text=Penalty%20amounts%E2%80%8B,State%20Government%20and%20increase%20annually.) when you overstay! On average, `$1,263,684` were paid just for the fines in Lonsdale Street!

# Along Lonsdale Street, which locations do most vehicles overstay in?

```{r parking-violation}
parking2019_vio <- parking2019_tidy %>%
  filter(InViolation == "true")
```

```{r}
parking2019_vio %>%
  group_by(BetweenStreet1) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  kable(caption = "Adjacent streets with the most restriction violations") %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```

> Out of the all five streets, Exhibition Street had the most number of vehicles which violated the time restriction.
> Exhibition St and Russel St are actually right next to one another! What do they have in common? (*elaborate*) - many rooftop bars etc.

```{r}
parking2019_vio %>%
  group_by(BetweenStreet1, Sign) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  kable(caption = "Top 10 most common parking signs which are violated") %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```

> We'd expect more vehicles to overstay in parking lots with a shorter time frame
> BUT, most vehicles overstayed in where the time restrictions were 2 hours

```{r}
parking2019_vio <- parking2019_vio %>%
  # Extract specfic signs, assign them according to minutes
  mutate(restrict_mins = case_when(
    str_starts(Sign, "1/2 P") ~ 30, 
    str_starts(Sign, "1P") ~ 60,
    str_starts(Sign, "2P") ~ 120),
  # Extract parking signs, assign them into respective factors 
    restriction = case_when(
    str_starts(Sign, "1/2 P") ~ "1/2P", 
    str_starts(Sign, "1P") ~ "1P",
    str_starts(Sign, "2P") ~ "2P"
    ),
    # Compute amount of mins overstayed
    overstay_mins = DurationMinutes - restrict_mins)
```

```{r}

require(ggridges)
ggplot(parking2019_vio) +
  geom_density_ridges(
    aes(
      x = overstay_mins,
      y = factor(restriction),
      fill = factor(restriction)
    ),
    alpha = 0.6,
    stat = "binline",
    bins = 45
  ) +
  scale_x_continuous(breaks = c(seq(from = 0, to = 300, by = 10)),
                     limits = c(0, 300)) +
  facet_wrap( ~ BetweenStreet1, nrow = 3) +
  scale_fill_manual(values = c("#663300", "#006633", "#330066")) +
  labs(x = "Minutes overstayed", y = "") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 12, 
                                    face = "bold", 
                                    margin = unit(c(1.5, 0, 0, 0), "lines"))) +
  ggtitle("Density estimate of vehicles who overstayed restrictions")
```

> No vehicles overstayed in the 1/2P signs in Queen St, Exhibition St& William St.

# Analysis 2: Arrival& Departure times of cars that overstayed
```{r}
parking2019_vio <- parking2019_vio %>%
  # Retrieve day of the week 
  mutate(arr_day = wday(arr_date, label = TRUE, week_start = 1),
         dep_day = wday(dep_date, label = TRUE, week_start = 1))
```

```{r}
parking2019_plot2 <- parking2019_vio 
# Format CHAR to TIME variable  
parking2019_plot2$arr_time <- 
  as.POSIXct(parking2019_plot2$arr_time, format="%H:%M")
parking2019_plot2$dep_time <-
  as.POSIXct(parking2019_plot2$dep_time, format="%H:%M")
parking2019_plot2 <- parking2019_plot2 %>%
  # Group arrival and departure times as arr_dep variable
    pivot_longer(c(arr_time, dep_time), 
               names_to = "arr_dep",
               values_to = "arr_dep_time")
```

```{r analysis2}
parking2019_plot2 %>% ggplot() +
  geom_violin(
    aes(x = arr_day, y = arr_dep_time, colour = arr_dep),
    scale = "count",
    alpha = 0.6,
    draw_quantiles = 0.5
  ) +
  facet_wrap(~ BetweenStreet1, nrow = 3) +
  scale_colour_manual(values = c("#00468b", "#009700")) +
  labs(x = "Arrival/Departure Time", y = "") +
  theme(legend.position = "bottom") 
```


```{r summary-violations}
summ_parking2019_vio <- parking2019_tidy %>%
  group_by(InViolation) %>%
  summarise(total = sum(n())) 
  
kable(summ_parking2019_vio,
      caption = "Proportion of vehicles in violation of parking restriction") %>%
  kable_styling(bootstrap_options = "bordered")
```

> Parking Services Officers may mark the tire of a vehicle parked in a time-restricted area& come back as soon as you overstay the time restriction.
> Inside Melbourne CBD, the parking fees for on street-parking is [$7/hr](https://www.melbourne.vic.gov.au/parking-and-transport/parking/parking-locations-fees/Pages/parking-locations-and-fees.aspx).

Data:
> In 2019, a total of 249,216 instances where a car parked& departed.
> Of this, 10,191 (2.918%) violated the restriction.
> This proportion may seem little, but parking fines are on average, [$124](https://www.melbourne.vic.gov.au/parking-and-transport/parking/parking-fines/Pages/default.aspx#:~:text=Penalty%20amounts%E2%80%8B,State%20Government%20and%20increase%20annually.) when you overstay! On average, `$1,263,684` were paid just for the fines in Lonsdale Street!


# Along Lonsdale Street, which locations do most vehicles overstay in?

```{r parking-violation}
parking2019_vio <- parking2019_tidy %>%
  filter(InViolation == "true")
```

```{r}
parking2019_vio %>%
  group_by(BetweenStreet1) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  kable(caption = "Adjacent streets with the most restriction violations") %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```

> Out of the all five streets, Exhibition Street had the most number of vehicles which violated the time restriction.
> Exhibition St and Russel St are actually right next to one another! What do they have in common? (*elaborate*) - many rooftop bars etc.

```{r}
parking2019_vio %>%
  group_by(BetweenStreet1, Sign) %>%
  summarise(n = n()) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  kable(caption = "Top 10 most common parking signs which are violated") %>%
  kable_styling(bootstrap_options = c("bordered", "striped"))
```

> We'd expect more vehicles to overstay in parking lots with a shorter time frame
> BUT, most vehicles overstayed in where the time restrictions were 2 hours

```{r}
parking2019_vio <- parking2019_vio %>%
  # Extract specfic signs, assign them according to minutes
  mutate(restrict_mins = case_when(
    str_starts(Sign, "1/2 P") ~ 30, 
    str_starts(Sign, "1P") ~ 60,
    str_starts(Sign, "2P") ~ 120),
  # Extract parking signs, assign them into respective factors 
    restriction = case_when(
    str_starts(Sign, "1/2 P") ~ "1/2P", 
    str_starts(Sign, "1P") ~ "1P",
    str_starts(Sign, "2P") ~ "2P"
    ),
    # Compute amount of mins overstayed
    overstay_mins = DurationMinutes - restrict_mins)
```

```{r}
require(ggridges)
ggplot(parking2019_vio) +
  geom_density_ridges(
    aes(
      x = overstay_mins,
      y = factor(restriction),
      fill = factor(restriction)
    ),
    alpha = 0.6,
    stat = "binline",
    bins = 45
  ) +
  scale_x_continuous(breaks = c(seq(from = 0, to = 300, by = 10)),
                     limits = c(0, 300)) +
  facet_wrap( ~ BetweenStreet1, nrow = 3) +
  scale_fill_manual(values = c("#663300", "#006633", "#330066")) +
  labs(x = "Minutes overstayed", y = "") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none") +
  theme(axis.title.x = element_text(size = 12, 
                                    face = "bold", 
                                    margin = unit(c(1.5, 0, 0, 0), "lines"))) +
  ggtitle("Density estimate of vehicles who overstayed restrictions")
```

> No vehicles overstayed in the 1/2P signs in Queen St, Exhibition St& William St.


# Analysis 2: Arrival& Departure times of cars that overstayed
```{r}
parking2019_vio <- parking2019_vio %>%
  # Retrieve day of the week 
  mutate(arr_day = wday(arr_date, label = TRUE, week_start = 1),
         dep_day = wday(dep_date, label = TRUE, week_start = 1))
```

```{r}
parking2019_plot2 <- parking2019_vio 

# Format CHAR to TIME variable  
parking2019_plot2$arr_time <- 
  as.POSIXct(parking2019_plot2$arr_time, format="%H:%M")
parking2019_plot2$dep_time <-
  as.POSIXct(parking2019_plot2$dep_time, format="%H:%M")

parking2019_plot2 <- parking2019_plot2 %>%
  # Group arrival and departure times as arr_dep variable
    pivot_longer(c(arr_time, dep_time), 
               names_to = "arr_dep",
               values_to = "arr_dep_time")
```

```{r analysis2}
parking2019_plot2 %>% ggplot() +
  geom_violin(
    aes(x = arr_day, y = arr_dep_time, colour = arr_dep),
    scale = "count",
    alpha = 0.6,
    draw_quantiles = 0.5
  ) +
  facet_wrap(~ BetweenStreet1, nrow = 3) +
  scale_colour_manual(values = c("#00468b", "#009700")) +
  labs(x = "Arrival/Departure Time", y = "") +
  theme(legend.position = "bottom") 
```

# Section 2 : What are the time frames where parking lots are the most vacant/occupied?

```{r read}
parking2019_tidy <- read.csv(here::here("parking2019_tidy.csv")) %>% 
<<<<<<< HEAD
  mutate(sign_rule = strtrim(Sign, 6), arr_date = date(arr_date))

```

```{r}
# Just for information of parking Sign (no need to include in shiny)
parking2019_tidy %>% 
  group_by(Sign) %>% 
  summarise(sign = n())
=======
  mutate(sign_rule = strtrim(Sign, 6))
>>>>>>> 7d115220b6cd59b2eeeeef608b7bd279fba2178f
```


```{r plot-temporal-patterns}
parking2019_tidy %>%
  group_by(arr_date, sign_rule, BetweenStreet1) %>%
  summarise(mean_duration = mean(DurationMinutes)) %>%
  ggplot(aes(x = as.Date(arr_date),
             y = mean_duration,
             group = sign_rule)) +
  geom_line(size = 0.3) +
  facet_grid(sign_rule ~ BetweenStreet1,
             # this code presents the facets in a nice way
             labeller = labeller(SignPlateID = label_wrap_gen(20))) +
  # this code mades the x axis a bit nicer to read
  scale_x_date(date_labels = "%d %b %Y",
               date_minor_breaks = "1 month") +
  scale_colour_brewer(palette = "Set2") +
  labs(x = "Date Time") +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(legend.position = "none")
```

> Some dates have unusual high duration of parking. It can be related to some holidays when people tend to park longer than usual. 
> William street with sign rule 1P MTR has the highest average of parking duration among other "between streets".


```{r avgduration_sign}
parking2019_tidy %>% 
  group_by(sign_rule) %>%
  summarise(avg_duration = mean(DurationMinutes)) %>%
  kable() %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```

```{r avgduration_betweenstreet}
parking2019_tidy %>% 
  group_by(BetweenStreet1) %>%
  summarise(avg_duration = mean(DurationMinutes)) %>%
  kable() %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```

# Section 3 : Parking availability: On a workday/non-workday, what are the time frames where parking lots are the most vacant/occupied? 


```{r holiday2019} 
hols_2019 <- tsibble::holiday_aus(year = 2019, state = "VIC")
#create dataset for holidays related to arr_date
park_2019_hols <- parking2019_tidy %>% 
  mutate(weekday = wday(arr_date, label = TRUE, week_start = 1),
         workday = if_else(
           condition = arr_date %in% hols_2019$date | weekday %in% c("Sat", "Sun"),
           true = "holidays",
           false = "workday"))
```

```{r workdays-vs-non-work}
ggplot(park_2019_hols,
       aes(x = as.factor(arr_hour),
           y = DurationMinutes,
             # Because there are duplicate date in different months, so we use this
           colour = sign_rule) 
       )+
  geom_boxplot(size = 0.3,
            alpha = 0.8) +
  facet_grid(sign_rule~workday,
             labeller = labeller(StreetName = label_wrap_gen(20))) +
  scale_colour_brewer(palette = "Set2", name = "sign_rule") +
  scale_y_continuous(breaks = c(seq(from = 0, to = 200, by = 20)),
                     limits = c(0, 200)) +
  theme(legend.position = "none")+
  labs(x = "Time Hour")
```

> On workdays, average duration of parking is high in the first hour of allowed time (i.e. 07.00 from the 07.00-20.00 parking time) and decline along the day. On the other hand, on holidays average duration of parking is quite fluctuated during the day in several spots of Lonsdale street. 
> People tend to stick with the rule when the parking spot has meter system, the average parking duration in the meter spots is lower than the allowed time.  
> Average duration of parking in non-meter parking spot tend to over the allowed time especially in the holidays.


```{r calendar-plot}
russel_cal <- park_2019_hols %>%
  frame_calendar(x = arr_hour,
                 y = DurationMinutes,
                 date = arr_date)

gg_cal <- russel_cal %>% 
  ggplot(aes(x = .arr_hour,
             y = .DurationMinutes,
             colour = as.factor(workday),
             group = arr_date)) +
            labs(colour = "Year")+
  geom_line()

prettify(gg_cal) +
  theme(legend.position = "bottom")
```

> Unusual pattern of parking duration occurs mostly on holidays, such as: 
10 June 2019 when people celebrate Queen's birthday,
20-21 long easter holiday,
25 April which is Anzac Day,
5 November when people enjoys Melbourne Cup,
25-26 Desember which is christmas holidays.

> For working days, Jan and Feb has lower parking duration than other months. However, we don't have any information for the possible reasons.

```{r process-parking-data}
park19_lm <- park_2019_hols %>% 
  mutate_at(.vars = vars(StreetName,
                         SignPlateID,
                         sign_rule,
                         arr_hour,
                         workday,
                         BetweenStreet1
                          ),
            as_factor) %>% 
  mutate(log_duration = log1p(DurationMinutes))
```


```{r fit-lm}
park_fit_lm <- lm (
  formula = log_duration ~ arr_hour + weekday + SignPlateID + sign_rule + BetweenStreet1,
  data = park19_lm
)

# statistic variables
park_fit_lm
```

```{r glance-fit-lm}
# Extract model fit summary
glance(park_fit_lm)
```

> Our model shows correlation between arrival time (hour) with duration of parking. To enhance the model we also include weekday/holidays, betweenStreet, parking rules as explanatory variables of the parking duration. However, the relationship is still not significant with r.squared only has 0.13. The reason of this is many variables that can explain the duration are not covered in the dataset, for example facilities near the parking spots (school, office, church, restaurant, mall/grocery shop) and people's motives (i.e. picking up passengers, waiting a friend).   


# Section 4 : There any prominent characteristics for the top 10 hardest parking street to get in Melbourne CBD?  **we need a new dataset here**

```{r top-10}
print_table <- function(table, head){
  table %>%
  group_by(StreetName, BetweenStreet1, BetweenStreet2) %>%
  summarise(CountperDay= n()/365) %>%
   arrange(desc(CountperDay)) %>%
  head(head)
}
save_table <- print_table(parking2019, 10)
write_csv(save_table, "Top10_Melb_Count.csv")

top10_table <- read_csv("Top10_Melb_Count.csv")
knitr::kable(top10_table, caption = "Top 10 busiest parking street in Melbourne") %>%
kableExtra::kable_styling(bootstrap_options = "basic")

```

```{r bincol-cor-info}
coord <- data_frame("lat" = c(-37.8147255,
                              -37.8192437,
                              -37.8101661,
                              -37.8183015,
                              -37.8156404,
                              -37.809040,
                              -37.8140175,
                              -37.8153781,
                              -37.8075632,
                              -37.816335),
                    "lon"=c(144.952553,
                            144.9553465,
                            144.9687394,
                            144.9811929,
                            144.976875,
                            144.969121,
                            144.9692056,
                            144.9531639,
                            144.9532773,
                            144.978169))

info <- data_frame("info" = c("Lonsdale Street is one of the main streets in Melbourne's CBD. It offers high rise apartment style living, in amongst the areas businesses, shopping centres and hotels. China Town extends through a number of smaller alleys between Lonsdale and Bourke.",
"King Street is a key hub of Melbourne's nightlife and is home to many pubs, nightclubs, restaurants, and adult entertainment venues",
"Lonsdale Street is one of the main streets in Melbourne's CBD. It offers high rise apartment style living, in amongst the areas businesses, shopping centres and hotels. China Town extends through a number of smaller alleys between Lonsdale and Bourke.",
"Jolimont Street features parks, business precincts and a limited amount of residential accommodation. It's close to Fitzroy Garden and Melbourne Cricket Ground",
"Jolimont Street features parks, business precincts and a limited amount of residential accommodation. It's close to Fitzroy Garden and Melbourne Cricket Ground",
"In Exhibition Street there a lot of luxurious hotels eg Marriott Hotel & Rydges Hotel. It also the heart of working district",
"In Exhibition Street there a lot of luxurious hotels eg Marriott Hotel & Rydges Hotel. It also the heart of working district",
"King Street is a key hub of Melbourne's nightlife and is home to many pubs, nightclubs, restaurants, and adult entertainment venues",
"William Street is a major street in the city, there are notable landmarks on William Street include the Queen Victoria Market, the Flagstaff Gardens, Immigration Museum, Supreme Court of Victoria, AMP Square",
"Wellington Parade South, it's located between parks and residential building"))

top10_cor_info <- bind_cols(top10_table, coord, info)
write_csv(top10_cor_info, "Top10_Melb_Cor_Info.csv")
```

```{r leaflet_markers}
top10_leaflet <- read_csv("Top10_Melb_Cor_Info.csv")

getColor <- function(table) {
  sapply(table$CountperDay, function(CountperDay) {
  if(CountperDay <= 350) {
    "green"
  } else if(CountperDay <= 450) {
    "orange"
  } else {
    "red"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(top10_leaflet)
) 

l <- leaflet(data = top10_leaflet[1:10,])

l %>%
addTiles() %>%
addAwesomeMarkers(~lon, ~lat, icon=icons, popup = ~as.character(info), label=~as.character(StreetName))
```


